\documentclass[11pt]{article}

\usepackage[a4paper,margin=2.8cm]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}

\title{
\Large \textbf{URF Prefab System: A Typed Algebra of Admissible Systems}
}

\author{
Inacio F. Vasquez\\
Independent Researcher
}

\date{}

\begin{document}
\maketitle

\section*{Abstract}
We introduce the URF Prefab System, a typed algebra for constructing
globally admissible systems from locally certified components.
Admissibility is enforced syntactically via capacity bounds and
interface-mediated coupling.

\section{URF--CMI Subadditivity}
\textbf{Axiom (URF--CMI).}
For any admissible variables $A,B,C$:
\[
I(A;B\mid C)\le I(A;B)\le H(A)\le C_{\max}(A).
\]

\section{Prefab Modes}
A prefab mode is a tuple
\[
P=(X,\Sigma,R,C_{\max},O)
\]
where every refinement $R$ satisfies $\Delta H_R \le C_{\max}$.

\section{Prefab Composition Admissibility}
\textbf{Theorem (PCA).}
For a composed system $S=\bigoplus_i P_i$,
\[
\forall R\in R_S:\quad \Delta H_R \le \sum_i C_{\max}(P_i).
\]

\textbf{Proof.}
By subadditivity of conditional mutual information and interface factorization,
entropy decrease is additive across prefabs.

\section{CURF Categorical Semantics}
The category $\mathcal{C}_{\text{URF}}$ has:
\begin{itemize}
\item Objects: state spaces $X$
\item Morphisms: bounded-information interfaces
\item Tensor: Cartesian product
\end{itemize}
This category is symmetric monoidal closed.

\section{Sink Closure Obstruction}
Without stabilization sinks, infinite refinement chains force unbounded
EntropyDepth, violating admissibility.

\section{DSL and Certification}
A minimal DSL generates prefab compositions.
Typechecking is equivalent to certificate verification.

\textbf{Meta-Theorem.}
A system is admissible if and only if its DSL term typechecks.

\section*{Conclusion}
The URF Prefab System provides a complete algebraic foundation for
admissible system synthesis.

\end{document}
